---
title: "Introduction to Making Presentation Slides \n with Xaringan"
author: "Shunkei Kakimoto" 
subtitle: APEC Skill Seminar
output:
  xaringan::moon_reader:
    css: "xaringan-themer.css"
    # css: "svm-xaringan-style.css"
    # css: "modified-svm-xaringan-style.css"
    lib_dir: libs
    nature:
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: true
---
class: middle


```{r, include = F, cache = FALSE}
here::i_am("GitControlled/Recitation/1_Introduction/recitation1_slides.rmd")
```


```{r, child = 'setup.rmd', cache = FALSE}
```

```{r, child = 'PrepareResults.rmd', cache=FALSE}
```

.content-box-green[**A Useful tip:**]

hitting letter "o" key will give you a panel view of the slides

---
# Outline

1.Short introduction ()
2.Flavor of presentation slide 
3.How to make presentation slides with xaringan?

+ How does it work? 

4.xaringanExtra

---
class: middle

## Source materials for this session: 

+ 


R Markdown: The Definitive Guide [here](https://bookdown.org/yihui/rmarkdown/)

+ `r Citet(xie2018r, "deschenes2007economic")` ["R markdown: The definitive guide"](https://bookdown.org/yihui/rmarkdown/#ref-xie2015)


---
class: middle

How do you make your presentation slide?

+ Beamer?
+ Power Point?

xaringan presentation!

+ Especially, it works well if you want present your results with `R` or `python`. 

???
+ Well there are lots of options to make presentation slides. I think the most common ways is to 

+ We mostly create figures and tables with some 


---
class: middle

## What's is `xaringan` package?



---
class: middle


---
class: middle


For more details, see

[xaringan Presentations](https://bookdown.org/yihui/rmarkdown/xaringan.html)




---
class: inverse, center, middle
name: intro

# Flavor of xiaringan presentation

<html><div style='float:left'></div><hr color='#EB811B' size=1px width=796px></html>

???
+ Well there are tons of useful functionalities in xiaringan package. 
+ Here, I would like to introduce the flavor of xaringan presentation with my slides I used for my recitation session.

---
class: middle

# Math

Almost the same syntax as in `Latex` 

.content-box-green[**Example (1) Inline math expressions**]:
```
$\omega_1=(6,10)$ and $\omega_2=(6,0)$
```
yields

$\omega_1=(6,10)$ and $\omega_2=(6,0)$

<br>

.content-box-green[**Example (2) Equation**]

```
$$U_j(x_j, y) = x_j + \theta_j ln \, y$$
```

yields

$$U_j(x_j, y) = x_j + \theta_j ln \, y$$

---
class: middle

.content-box-green[**Example (3) Equation**]
```
\begin{aligned}
\max_{x_1,y_1} \quad & U_1(x_1, y_1)=x_1y_1 \\
\textrm{s.t.} \quad & max[x_2, y_2] = \overline{u_2} \\
  & x_1 + x_2 = 16 \\
  & y_1 + y_2 = 16
\end{aligned}
```

yields

\begin{aligned}
\max_{x_1,y_1} \quad & U_1(x_1, y_1)=x_1y_1 \\
\textrm{s.t.} \quad & max[x_2, y_2] = \overline{u_2} \\
  & x_1 + x_2 = 16 \\
  & y_1 + y_2 = 16
\end{aligned}


---
class: middle

## Figures



---
class: middle

## Figures: map with `leaflet`

.medium-code[
.panelset[ 
<!-- Map 1 -->
.panel[.panel-name[Code for Map 1]
```{r, echo=TRUE}
if (!require("pacman")) install.packages("pacman")

# === For example the boundary of MN=== #
pacman::p_load("tigris", "sf", "dplyr", "tmap", "leaflet")

# --- Download shapefile for MN --- #
mn_bd <- 
  states(cb = FALSE, ) %>%
  filter(STUSPS=="MN")

# --- Visualization with leaflet --- #
map_mn_bd <- 
  tmap_leaflet(
    tm_shape(mn_bd)+
    tm_borders(col="blue") +
    tm_text("STUSPS", size = 2)
  ) %>%
  addTiles(group = "Esri.WorldTopoMap")
```
  ]

.panel[.panel-name[Map 1]
```{r}
map_mn_bd
```
  ]

.panel[.panel-name[Code for Map 2]

```{r, echo=TRUE}
# === Digital map of aquifer boundary for the High Plains aquifer === #
# Download the data from the website of USGS

# download.file(
#   url = "https://www.sciencebase.gov/catalog/file/get/6314061bd34e36012efa397b?f=__disk__39%2F00%2Fb6%2F3900b621917a747319cd00a5ecb647623a500dae", 
#   here("Data/hpa_bd.zip")
#   )

# unzip(
#   zipfile = here("Data/hpa_bd.zip"),
#   exdir = here("Data/hpa_bd")
#   )

hpa_bd <- 
  st_read("Data/hpa_bd/hp_bound2010.shp")


```





]
]

---
class: middle

## Tables

<!-- Linear regression table -->



---
class: middle

## Animation with `gganimate`

.content-box-green[**Example (1): Relationship between CDF and PDF**]
+ **From CDF to PDF**: $f(x) = \frac{d}{dx}F(x)$ </br> (by definition of PDF)

+ **From PDF to CDF**: $F(x) = Pr(X \leq x) = \int_{-\infty}^x f(t) dt$ </br> (as shown below)


```{r, dpi=36, cache=F, echo=F, out.width = "80%"}
new_gif
```

---
class: middle

.content-box-green[**Example (1): Relationship between CDF and PDF**]


```{r}
animate(p1_annimate, fps = 20, duration = 5)
```


---
class: inverse, center, middle
name: intro

# How to make presentation slides with xaringan

<html><div style='float:left'></div><hr color='#EB811B' size=1px width=796px></html>
---



---
class: middle




